### 2022-10-20 Editing_and_Exploring.Rmd
edit
progress

**Loading the dataset:**  
```{r}
library(tidyverse)
pokemon <- read.csv("pokemon.csv")
head(pokemon)
```

@@

>>>>

**Loading the dataset:**  
```{r}
library(tidyverse)
pokemon <- read.csv("data/pokemon.csv")
head(pokemon)
```

@@

ability_split <-strsplit(as.character(pokemon$abilities),',',fixed=TRUE)
#ability_split
```

```{r}
ability_df <- tibble(line = 1:801, text = pokemon$abilities)
ability_df
```
